Finite-state morphological transducers for three Kypchak languages

### 2013-10-24 kipchak-lrec-2013/kipchak-paper.tex
another FIXME
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@48164 72bbbca6-d526-0410-a7d9-f06f51895060
a map of Kypchak
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@48174 72bbbca6-d526-0410-a7d9-f06f51895060

%FIXME: update for the three languages
The tagset consists of 127 separate tags, 19 covering the main parts of speech (noun, verb, adjective, adverb, postposition, etc.) and 108 covering morphological subcategorisation for e.g. case, number, person, possession, transitivity, tense-aspect-mood, etc. The tags are represented as multicharacter symbols, between less than `<' and greater than `>' symbols. The tagset is quite extensive and still not entirely stabilised, as such a full listing is not included here. However, the tags are listed in the source code of the transducer,\footnote{\url{https://apertium.svn.sourceforge.net/svnroot/apertium/branches/apertium-kir/}} along with comments describing their usage.

@@

\begin{table}
\begin{center}
\begin{tabular}{llrr}
\toprule
\textbf{Language} & \textbf{Corpus} & \textbf{Words} & \textbf{Coverage} \\
\midrule
\multirow{4}{*}{Kazakh} & Wikipedia 2013 &  -  &  - \\
	& RFE/RL 2010 & 3.2M & - \\
	& Bible & 577K & - \\\cline{2-4}
	& Average & - & 90.5\% \\
\midrule
\multirow{4}{*}{Tatar} & Wikipedia 2013 & 128K &  - \\
	& RFE/RL 2005--2011 & 4.6M & - \\
	& New Testament & 137K & - \\\cline{2-4}
	& Average & - & 89.0\% \\
\midrule
\multirow{3}{*}{Kumyk} & Yoldaš & 287K &  - \\
	& New Testament & 154K & - \\\cline{2-4}
	& Average & - & 90.1\% \\
\bottomrule
\end{tabular}
 \caption{Corpora used for naïve coverage tests}
 \label{table:corpora}
\end{center}
\end{table}

>>>>

%FIXME: update for the three languages
The tagset consists of 127 separate tags, 19 covering the main parts of speech (noun, verb, adjective, adverb, postposition, etc.) and 108 covering morphological subcategorisation for e.g. case, number, person, possession, transitivity, tense-aspect-mood, etc. The tags are represented as multicharacter symbols, between less than `<' and greater than `>' symbols. The tagset is quite extensive and still not entirely stabilised, as such a full listing is not included here. However, the tags are listed in the source code of the transducer,\footnote{\url{https://apertium.svn.sourceforge.net/svnroot/apertium/branches/apertium-kir/} testing} along with comments describing their usage.

@@

\begin{table}
\begin{center}
\begin{tabular}{llrr}
\toprule
\textbf{Language} & \textbf{Corpus} & \textbf{Words} & \textbf{Coverage} \\
\midrule
\multirow{4}{*}{Kazakh} & Wikipedia 2013 &  -  &  - \\
	& RFE/RL 2010 & 3.2M & - \\
	& Bible & 577K & - \\\cline{2-4}
	& Average & - & 90.5\% \\
\midrule
\multirow{4}{*}{Tatar} & Wikipedia 2013 & 128K &  - \\
	%FIXME: the News corpus isn't RFERL, pretty sure; maybe we should test just on RFERL content?
	& News 2005--2011 & 4.6M & - \\
	& New Testament & 137K & - \\\cline{2-4}
	& Average & - & 89.0\% \\
\midrule
\multirow{3}{*}{Kumyk} & Yoldaš & 287K &  - \\
	& New Testament & 154K & - \\\cline{2-4}
	& Average & - & 90.1\% \\
\bottomrule
\end{tabular}
 \caption{Corpora used for naïve coverage tests}
 \label{table:corpora}
\end{center}
\end{table}
